Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}

### 2014-04-29 Paper.tex
PoC-4
More fixes.

\title{Ethereum: A Secure Decentralised Generalised Transaction Ledger}
\author{
    Dr. Gavin Wood\\
    Co-Founder \& CTO, Ethereum Project\\
    gavin@ethereum.org
}
\begin{document}

@@

The gas is reduced by the instruction's gas cost and for most instructions, the program counter increments on each cycle, for the three exceptions, we assume a function $J$, subscripted by one of two instructions, which evaluates to the according value:
\begin{eqnarray}
\boldsymbol{\mu}'_{g} & \equiv & \boldsymbol{\mu}_{g} - C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \\
\boldsymbol{\mu}'_{pc} & \equiv & \begin{cases}
J_o(\boldsymbol{\mu}) & \text{if} \quad w \in \{ \text{\small JUMP, JUMPI} \} \\
\boldsymbol{\mu}_{pc} + p & \text{if} \quad w \in [\text{\small PUSH1}, \text{\small PUSH32}] \\
\boldsymbol{\mu}_{pc} + 1 & \text{otherwise}
\end{cases}
\end{eqnarray}

>>>>

\title{Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{Proof-of-Concept V}}}
\author{
    Dr. Gavin Wood\\
    Co-Founder \& CTO, Ethereum Project\\
    gavin@ethereum.org
}
\begin{document}

@@

The gas is reduced by the instruction's gas cost and for most instructions, the program counter increments on each cycle, for the three exceptions, we assume a function $J$, subscripted by one of two instructions, which evaluates to the according value:
\begin{eqnarray}
\quad \boldsymbol{\mu}'_{g} & \equiv & \boldsymbol{\mu}_{g} - C(\boldsymbol{\sigma}, \boldsymbol{\mu}, I) \\
\quad \boldsymbol{\mu}'_{pc} & \equiv & \begin{cases}
J_{\text{JUMP}}(\boldsymbol{\mu}) & \text{if} \quad w = \text{\small JUMP} \\
J_{\text{JUMPI}}(\boldsymbol{\mu}) & \text{if} \quad w = \text{\small JUMPI} \\
\boldsymbol{\mu}_{pc} + p & \text{if} \quad w \in [\text{\small PUSH1}, \text{\small PUSH32}] \\
\boldsymbol{\mu}_{pc} + 1 & \text{otherwise}
\end{cases}
\end{eqnarray}
